Manuscript

### 2015-02-03 inst/simulation/manuscript.Rmd
...

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "T", "TA", "FMP"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r figure-3-init}
getPopulationSizes <- function(scenarios, modelNames, populationSizeOverEstimate=Inf) {
  study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
  validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
  populationSizes <- validation$getValidationTemporalPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  #validation$summarizePopulationSize(populationSizes)  
}

@@

```{r figure-3-init-2}
registerDoMC(cores=10) # The nodes seem to run out of memory and fail with a bogus error message, so it's better to reduce the number of used cores.
populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)

registerDoMC(cores=detectCores())

@@

>>>>

prettyScenario <- function(scenario) substr(scenario, 1, 1)
prettyModelName <- function(x) {
  lookup <- data.frame(x=modelNames, y=c("ST", "TF", "T", "FMP"), stringsAsFactors=F)
  lookup$y[match(x, lookup$x)]
}

@@

```{r figure-3-init}
getIntersections <- function(scenarios) {
  study <- getStudy(scenario="A")
  validation <- Validation(study=study)
  intersections <- validation$getValidationTemporalIntersections(scenarios=scenarios)
  intersections$Year <- intersections$year
  intersections
}

getPopulationSizes <- function(scenarios, modelNames, populationSizeOverEstimate=Inf) {
  study <- getStudy(scenario="A") # Get study object, scenario doesn't matter
  validation <- Validation(study=study, populationSizeOverEstimate=populationSizeOverEstimate)
  populationSizes <- validation$getValidationTemporalPopulationSizes(scenarios=scenarios, modelNames=modelNames)
  #validation$summarizePopulationSize(populationSizes)  
}

@@

```{r figure-3-init-2}
registerDoMC(cores=10) # The nodes seem to run out of memory and fail with a bogus error message, so it's better to reduce the number of used cores.
populationSizes <- getPopulationSizes(scenarios=scenarios, modelNames=modelNames)
populationSizes2000 <- getPopulationSizes(scenarios=paste0(scenarios, "combined"), modelNames=modelNames)
populationSizes10Days <- getPopulationSizes(scenarios=paste0(scenarios, "10days"), modelNames=modelNames)
registerDoMC(cores=detectCores())

@@

```{r table-2}
intersections <- getIntersections(scenarios)
intersections2000 <- getIntersections(scenarios=paste0(scenarios, "combined"))
intersections10days <- getIntersections(scenarios=paste0(scenarios, "10days"))
intersections <- plyr::join(populationSizes, intersections)
intersections2000 <- plyr::join(populationSizes2000, intersections2000)
intersections10days <- plyr::join(populationSizes10Days, intersections10days)
i.stat <- function(x) data.frame(i.mean=round(mean(x$intersections/x$Observed),2), i.sd=round(sd(x$intersections/x$Observed),2))
ddply(intersections, .(Scenario), i.stat)
ddply(intersections2000, .(Scenario), i.stat)
ddply(intersections10days, .(Scenario), i.stat)
```
